---
title: "Harmonization"
author: "Vaughn Johnson"
output: html_document
---

# The inadequacies of previous efforts
Over the summer, I tried to make a general purpose harmonization function
which would take a series of key-value pairs and the like, and transform
an arbitrary data source to meet the format we need to perform meaningful
merging later on. I had some success in this, but it was hard to be sure 
I was meeting all of the cases we encountered in the data.

But then we finally made tables of the unique values found in the data! This
opened up a treasure trove cases I had previously missed, and let me further
harmonize the data. It always opened up new classes of things which can be
harmonized, which lend themselves to being projects in 2019.

## Harmonizing Nulls
Probably the largest discovery / improvement to scraping was [the harmonization 
of nulls](https://github.com/statnet/ffsg/blob/1d7d3450b130964676f2f747088a71c197678638/Data/ffsgData/R/Harmonizer.R#L107). In my previous designs, I had made the assumption that each data source,
even if they did use the standard `NA` used to denote `NULL` in R, still were
self-consistent with their use of that non-standard encoding. After tabling the
data, it was apparent this was not the case, and so I revised the harmonization
code to accpet a general list of encodings which all map to `NA`. This was most
helpful in the fields for names and races.

## Research into `!!!`
In the code I wrote over the summer, I had copied and pasted some code from 
StackOverflow which, while it worked (e.g., `mutate(race = recode(race, !!!race_encoding)) %>%`,
referenced [here](https://github.com/statnet/ffsg/blob/1d7d3450b130964676f2f747088a71c197678638/Data/ffsgData/R/Harmonizer.R#L114)). What I did not understand was what the `!!!` operator accomplished. 
I now understand that this operator is something really only makes sense in the
context of R. 

R allows one to have a list of named parameters, e.g.

```{r}
foo <- function(bar, baz) {print(bar - baz)}
```
The first argument is named `bar`, and the second is named `baz`. One can call 
`foo()` in several ways

1. `foo(1, 2)`
2. `foo(bar=1, baz=2)`
3. `foo(baz=2, bar=1)`

In other words, R understands that parameters have names, and in the call of
the function, if the name of the parameter is specified, the order doesn't
matter. What this means in the context of my code is that for the line 

```{r, eval=F}
 mutate(race = recode(race, !!!race_encoding)) %>%
```

`!!!` expands the list `race_encoding` to that list's keys as paramter names,
and values as argument. For example, if `race_encoding = list('foo'='bar')`,
then `mutate(race = recode(race, !!!race_encoding)) %>%` would evaluate to 
`mutate(race = recode(race, foo=bar)) %>%`. This is really a huge win for 
software engineering here, because it means we can use `recode` with any
general key-value pair without worrying about specifying which variables map to 
which parameters.


## Canon columns, and future work
Right now, we assume that the three data sources share several fields:
```{eval=F}
name: The name of the victim
age:  The age of the victim
sex:  The gender of the victim
race: The race of the victim
date: The date of the victim's death
zip:  The zipcode of the victim's death
```
These are the fields which were used for merging. Unfourtunately, Killed By Police
does not have zip code, so I simply removed the check which makes sure that any
data source being harmonized has at least these columns. When revisions are made
to the merging part of `ffsgData`, this might be a sticking point.
