---
title: "Linkage"
author: "Vaughn Johnson"
date: "4/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Trying to Link WaPo with KBP

## Setup
```{r, echo=TRUE, include=FALSE}
library(dplyr)
library(here)
library(RecordLinkage)

path_to_src = here::here(file.path('R'))
load(file.path(path_to_src,
               "HarmonizedFiles",
               "HarmonizedDataSets.RData"))

common_cols = intersect(colnames(kbp_harmonized),
                        colnames(wapo_harmonized))

common_cols = c("name")
 kbp_link = kbp_harmonized %>% select(common_cols) %>% filter(!is.na(name))
wapo_link = wapo_harmonized %>% select(common_cols) %>% filter(!is.na(name))
```

## Confirm at least one observation is shared
```{r}
intersecting_names = intersect( kbp_harmonized$name,
          wapo_harmonized$name)

head(intersecting_names)


# Terry Lee Cockrell is in intersection
'Terry Lee Cockrell' %in% intersecting_names

 kbp_harmonized %>% filter(name == "Terry Lee Cockrell")
wapo_harmonized %>% filter(name == "Terry Lee Cockrell")
```

## Trying Linkage
```{r}
links = compare.linkage(kbp_link, wapo_link,
                        #blockfld = c('state'), 
                        phonetic = T)

# Build similarity weights
# between 0 and 1 for each candidate pair
results = emWeights(links)

table(results$pairs)
```

This is where we begin to run into problems:

- The probabilities of a pair being a nonmatch (`results$U` in results) are all `NaN`
- Huge amount of missing data means we never seem to have a real number for "is_match"
- m-probabilities only go to like 128, so `results$M` is far shorter than the number of pairs

