devtools::use_vignette("my-vignette")---
title: "Missingness"
author: "Vaughn Johnson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

FFSG has currently collected data from 4 data sources

1. The US Census
2. Fatal Encounters
3. Mapping Police Violence
4. Killed By Police

The first data source is, generally speaking, complete and valid. Our challenge
lies in the remaining three. Each data set contains information on police violence,
where each row in the data set is a person who was killed by police, with information
related to the deceased such as sex, race, age, as well as information
relevant to their death, such as time of death and location. The challenge of
collecting and harmonizing these three data sets so they follow similar coding
and naming conventions is accomplished in the `Harmonizer.R` and `MasterScraper.R`
files. The sraped and harmonized dataframes are stored in the `HarmonizedFiles`
directory. To refresh these documents, simply `source(Harmonizer.R)`.

## The Goal
This document seeks to address the next problem, which is missingness
between these three datasets. We want to uncover if there are any mechanisms
behind missingness, and use that information to inform how we can impute missing 
values, and also help with merging the three data sets.

# The Datasets

```{r, results="hide", message=FALSE}
library(here)
library(DT)
library(tidyr)

source(here::here(file.path('R', 'Harmonizer.R')))
load(here::here(file.path("R", "HarmonizedFiles","HarmonizedDataSets.RData")))

fe  =  fe_harmonized
mpv = mpv_harmonized
kbp = kbp_harmonized

```

Here are the three data scoures on Police Violence

|Name|Abbreviation|Source URL|Live or archival|
|---|---|---|---|---|---|---|---|
|Killed By Police|`kbp`|[link](http://www.killedbypolice.net/)|Archival|
|Mapping Police Violence|`mpv`|[link](https://mappingpoliceviolence.org/s/MPVDatasetDownload.xlsx)|Live|
|Fatal Encounters|`fe`|[link](https://docs.google.com/spreadsheets/d/1dKmaV_JiWcG8XBoRgP8b4e9Eopkpgt7FL7nyspvzAsE/edit#gid=0)|Live|

And here's another table with information about the dimensionality of the datasets.

```{r, results="hide", echo=FALSE}
cols = c('Name',
         'Start Date',
         'End Date',
         'Number of Rows',
         'Number of Columns',
         'Fraction of dataset missing')

info_table = data.frame(matrix(nrow=3, ncol=length(cols)))

info_table = setNames(info_table, cols)

get_data_set_info <- function(dataset) {
    return( c(NA,
              min(dataset$date, na.rm = T),
              max(dataset$date, na.rm = T),
              nrow(dataset),
              ncol(dataset),
              sum(is.na(dataset)) / (nrow(dataset) * ncol(dataset))))
}

info_table[1, ] = get_data_set_info(mpv)
info_table[2, ] = get_data_set_info(kbp)
info_table[3, ] = get_data_set_info(fe)
info_table$Name = c("MPV", "KBP", "FE")
info_table[, c('Number of Rows', 'Number of Columns', 'Fraction of dataset missing')] =     lapply(info_table[, c('Number of Rows', 'Number of Columns', 'Fraction of dataset missing')], as.numeric)
info_table$`Fraction of dataset missing` = round(info_table$`Fraction of dataset missing`, 3)

info_table
```

```{r, results = "asis", echo=FALSE}
knitr::kable(info_table)
```

# Data Munging and Concatenation
To describe missingness a little better, I'm going to take the field which are
common between the three shooting datasets, and concatenate them, with an additional
column remembering which rows belong to which data sets.

```{r}
common_cols = c('source', 'name', 'age', 'sex', 'race', 'date')
fe['source'] = 'fe'
mpv['source'] = 'mpv'
kbp['source'] = 'kbp'

combined = rbind(fe[common_cols], mpv[common_cols], kbp[common_cols])

table(combined[c('source','race')], useNA = 'always') / sum(table(combined[c('source','race')], useNA = 'always'))
```
